<header style="text-align: center">

### 2019-05-22 report/report.Rmd
Analyze before/after event average flights, boxplot in report

>>>>

- Traffic before the attacks: `r floor(before[, mean(N.x + N.y)])` average daily flights (including departures and arrivals)
- Traffic after the attacks: `r floor(after[, mean(N.x + N.y)])` average daily flights (including departures and arrivals)

Even one month after the event, the traffic is still lower. Overall, the traffic is reduced in a `r format(abs((after[, mean(N.x + N.y)] - before[, mean(N.x + N.y)]) / before[, mean(N.x + N.y)]) * 100, digits = 3)`% following the tragic events. Further details can be extracted from the figure below:

```{r, fig.align='center'}
ggplot(data = NULL, aes(y = N.x + N.y)) +
	geom_boxplot(data = before, aes(x = 'Before')) +
	stat_summary(data = before, aes(x = 'Before'), fun.y = mean, geom = 'point', shape = 5, size = 2.5) +
	geom_boxplot(data = after, aes(x = 'After')) +
	stat_summary(data = after, aes(x = 'After'), fun.y = mean, geom = 'point', shape = 5, size = 2.5) +
	scale_x_discrete(limits = c('Before', 'After')) +
	labs(title = paste('Average Daily Flights at', bru), x = NULL, y = 'Number of Flights') +
	theme(plot.title = element_text(hjust = 0.5))
```
